Carbonate chemistry at Ny-Ålesund

### 2021-12-27 awipev-CO2.Rmd
modified ggreg

#################### Regression function
# function regression plot with equation (MA or OLS) in title
ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title", subtitle = "subtitle", xlab = "x", ylab = "y", proplot = TRUE, ...) 
  { # x and y are the names of the variables
  fit_data <- tibble(xdata, ydata)
  colnames(fit_data) = c("xdata", "ydata")
  fit <- print(lmodel2::lmodel2(ydata ~ xdata))
if (type == "OLS") ty = 1 #one selects OLS only
if (type == "MA") ty = 2 #one selects MA only
#reg <- fit$regression.results[ty,] #one selects OLS only
intercept <- fit$regression.results$Intercept[ty]
slope <- fit$regression.results$Slope[ty]
predicted <- fit$regression.results$Intercept[1] + xdata * fit$regression.results$Slope[1]
error <- xdata - predicted
if (plot == TRUE) {
  plt <- ggplot(data = fit_data, aes(x = xdata, y = ydata)) + 
  geom_point(na.rm = TRUE, size = 2, colour = "blue") +
  geom_abline(aes(intercept = intercept, slope = slope),
              colour = "blue")  + 
  labs(title = paste(title, 
                     "\ntype: ", type,
                     "; R2 = ", round(fit$rsquare, digits = 2),
                     "; Intercept =", signif(intercept, 3),
                     "; Slope =", signif(slope, 3),
                     "\nP =", signif(fit$P.param, 3),
                    "rmse =", signif(sqrt(mean(error^2, na.rm=TRUE)), 3)),
       subtitle = subtitle,
       x = xlab,
       y = ylab) +
#    lims(x = c(min(fit_data$xdata), max(fit_data$xdata)), y = c(min(fit_data$ydata), max(fit_data$ydata))) +
    theme_bw() +
    theme(plot.title = element_text(size = 7))
    if (proplot == TRUE) { # property-property plot
      plt <- plt +
        geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
        theme(aspect.ratio = 1)
    }
  return(list(plot = plt, fit = fit))
  } else {
  return(fit)
    }
}

@@

# # Many issue with sal_ctd_insi
# # read files made available by Philipp with  quality-controlled data
# https://doi.org/10.1594/PANGAEA.929583
# pg_data("10.1594/PANGAEA.929583")

@@

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
lm <- lm2(x = d_all$sal_insitu_ctd_10m, y = d_all$sal_fb)
p <-  ggplot(d_all, aes(x=sal_insitu_ctd_10m, y = sal_fb))+
  geom_point( aes(color=factor(monthd))) + 
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(lm$rsquare, 3),
                     "; Intercept =", signif(lm$intercept_MA, 3),
                     "; Slope =", signif(lm$slope_MA, 3),
                     "; P =", signif(lm$P, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
  coord_fixed(ratio = 1 )+
  labs( x="Salinity CTD 10 m", y="Salinity FB ", color = "Months") + theme_bw()

print(p) #p_sal_fb_ctd

@@

```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
title <- "pCO2 normalized at in situ temperature"
reg <- ggreg(
  xdata = d_all$pco2_fb_insi_temp,
  ydata = d_all$pco2_calc_fb_insi_temp,
  type = "MA",
  plot = TRUE,
  title = title,
  subtitle = "",
  xlab = "Measured pCO2",
  ylab = "Calculated pCO2",
  proplot = TRUE
)
p <- reg$plot
ggsave(filename = "figures/pco2_calc_meas.png", plot = p)
```

>>>>

#################### Regression function
# function regression plot with equation (MA or OLS) in title
ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title", xlab = "x", ylab = "y", proplot = TRUE, ...) 
  { # x and y are the names of the variables
  fit_data <- tibble(xdata, ydata)
  colnames(fit_data) = c("xdata", "ydata")
  fit <- print(lmodel2::lmodel2(ydata ~ xdata))
if (type == "OLS") ty = 1 #one selects OLS only
if (type == "MA") ty = 2 #one selects MA only
#reg <- fit$regression.results[ty,] #one selects OLS only
intercept <- fit$regression.results$Intercept[ty]
slope <- fit$regression.results$Slope[ty]
predicted <- fit$regression.results$Intercept[1] + xdata * fit$regression.results$Slope[1]
error <- xdata - predicted
if (plot == TRUE) {
  plt <- ggplot(data = fit_data, aes(x = xdata, y = ydata)) + 
  geom_point(na.rm = TRUE, size = 2, colour = "blue") +
  geom_abline(aes(intercept = intercept, slope = slope),
              colour = "blue")  + 
  labs(title = title,
       subtitle = paste("\ntype: ", type,
                     "; R2 = ", round(fit$rsquare, digits = 2),
                     "; Intercept =", signif(intercept, 3),
                     "; Slope =", signif(slope, 3),
                     "\nP =", signif(fit$P.param, 3),
                    "rmse =", signif(sqrt(mean(error^2, na.rm=TRUE)), 3)),
       x = xlab,
       y = ylab) +
#    lims(x = c(min(fit_data$xdata), max(fit_data$xdata)), y = c(min(fit_data$ydata), max(fit_data$ydata))) +
    theme_bw() +
    theme(plot.title = element_text(size = 10, face = "bold"),
          plot.subtitle = element_text(size = 8))
    if (proplot == TRUE) { # property-property plot
      plt <- plt +
        geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
        theme(aspect.ratio = 1)
    }
  return(list(plot = plt, fit = fit))
  } else {
  return(fit)
    }
}

@@

# # Many issue with sal_ctd_insi
# # read files made available by Philipp on 2021-12-09 with quality-controlled data
# # not useful as these are FerryBox data...
# https://dashboard.awi.de/?dashboard=3865
# Test with one of the files: https://doi.org/10.1594/PANGAEA.929583
# pg_data("10.1594/PANGAEA.929583")

@@

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
reg <- ggreg(
  xdata = d_all$sal_insitu_ctd_10m,
  ydata = d_all$sal_fb,
  type = "MA",
  plot = TRUE,
  title = "Comparison salinity",
  #subtitle = "",
  xlab = "Salinity CTD 10 m",
  ylab = "Salinity FB",
  proplot = TRUE,
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)),
  coord_fixed(ratio = 1)
)
print(reg$plot)

@@

```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
title <- "pCO2 normalized at in situ temperature"
reg <- ggreg(
  xdata = d_all$pco2_fb_insi_temp,
  ydata = d_all$pco2_calc_fb_insi_temp,
  type = "MA",
  plot = TRUE,
  title = title,
  #subtitle = "",
  xlab = "Measured pCO2",
  ylab = "Calculated pCO2",
  proplot = TRUE
)
p <- reg$plot
ggsave(filename = "figures/pco2_calc_meas.png", plot = p)
```
